### 2023-12-19 sections/1stratified.tex
Add files via upload

\begin{definition}\label{def:framed_d_under_n_sructure}
    The $\infty$-category of basics describing framed $\mathsf{D}_{d \subset n}$-manifolds is given by the pullback of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{D}_{d \subset n}^* \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{D_n^*} \simeq * \arrow[d] \\
            \mathsf{D}_{d \subset n} \arrow[r] & \mathsf{D}_n \simeq \mathsf{BO}(n).
        \end{tikzcd}
    \end{equation}
\end{definition}

>>>>

\begin{definition}\label{def:framed_d_under_n_structure}
    The $\infty$-category of basics describing framed $\mathsf{D}_{d \subset n}$-manifolds is given by the pullback of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{D}_{d \subset n}^* \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{D_n^*} \simeq * \arrow[d] \\
            \mathsf{D}_{d \subset n} \arrow[r] & \mathsf{D}_n \simeq \mathsf{BO}(n).
        \end{tikzcd}
    \end{equation}
\end{definition}

### 2023-12-19 sections/2homology.tex
Add files via upload

    In more details, following \cite[ex.2.5]{aft_fhstrat}, objects of $\disk(\bstr)_{/M}$ are finite sets of open embeddings of disks $(U \xhookrightarrow{} M)$. A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$. A multi-morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
\end{remark}

\begin{remark}
    The constructions of the slice category also holds, word for word, in the case of $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. The fact that they are $\infty$-operads is also true. The key difference is what the objects and multi-morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e. finite sets of open embeddings into $M$. However, the multi-morphisms now contain less information. A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. Similarly, for the multi-morphisms too.

    That is, a multi-morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both $\infty$-operads $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

@@

We now focus on describing disk algebras over oriented intervals with and without boundary. Not only is this an important example for what disk algebras look like, but it's also important in defining what it means to say that factorization homology is excisive. The following constructions can be found in the originals \cite{af_fhtop,aft_fhstrat}.

We want to show that disk algebras with $\mathsf{D}_1^{\partial, \mathsf{or}}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically. For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.

@@

\begin{proposition}\label{prop:disk1bor=assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories between $\mathsf{D}_1^{\partial, \mathsf{or}}$-structured disks and the symmetric monoidal envelope of $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow[\simeq]{\ \ [-] \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}}).
    \end{equation}
    %
    The functor $[-]$ assigns $[\hoint] = R$, $[\mathbb{R}] = A$ and $[\mathbb{R}_{\leq 0}] = L$.
\end{proposition}

@@

\begin{proposition}\label{prop:disk1bor_over_int=ORL}
    There are equivalences of $\infty$-operads
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
    \end{equation}
    %
    that descend to the equivalences of \cref{prop:disk1bor=assocRL}.
\end{proposition}

\begin{proof}
    As in the proof of \cref{prop:disk1bor=assocRL} the first equivalence is clear. The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$. These are then clearly the objects that map to the respective distinguished subsets. Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijections on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented. It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:env_ORL=env_assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories
    %
    \begin{equation}
        \mathsf{Env}(\mathsf{O^{RL}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env}(\disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}})
    \end{equation}
\end{proposition}

@@

    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, \mathsf{or}})$. There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty. This functor is final\footnote{A functor $F: \catC \xrightarrow{} \mathscr{D}$ between $\infty$-categories is final if precomposition with it preserves colimits \[ \mathsf{colim}(G \circ F) \simeq \mathsf{colim}(G).\]} because adjoining a minimum and maximum gives a left adjoint to it. We recognize the simplicial object
    %
    \begin{equation}
        \mathsf{B}_{\bullet}(R, A, L): \Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}} \simeq \mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC
    \end{equation}
    %
    as the two-sided bar construction. Since $\catC$ has colimits and $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ is final, the geometric realization of the above is
    %
    \begin{equation}
        R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
    \end{equation}
    %
    The naturality of this construction is immediate from the above presentation.
\end{proof}

%\begin{proposition}[{\cite[prop.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
%    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$. Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, \mathsf{or}}) \xrightarrow{} \catC$. Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
%    %
%    \begin{equation}
%        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
%    \end{equation}
%\end{proposition}

@@

\begin{proof}
    The definition comes with a claim that the canonical morphism in $\catC$ exists. This we need to show. The data of a collar-gluing $f: M \xrightarrow{} [-1,1]$ allows us to pushforward $F$ to
    %
    \begin{equation}
        f_*F: \disk (\mathsf{D}_1^{\partial, \mathsf{or}})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
    \end{equation}
    %
    By \cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$. Further using \cref{prop:barconst=intinterval} we have
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{f(M_0 \times \mathbb{R})}  F(M_+)\simeq \int_{[-1,1]} f_* F \xrightarrow{\quad} F (f^{-1}[-1,1]) = F(M),
    \end{equation}
    %
    where the morphism is given by the fact that factorization homology is a colimit.
\end{proof}

@@

    The first nontrivial example is then the oriented circle. We know that the algebras that we will be evaluating with are $\disk (\mathsf{D}_1^{\partial, \mathsf{or}})$-algebras (or even simpler the restriction to $\disk (\mathsf{D}_1^{\mathsf{or}})$ the ones without boundary). The oriented circle can be presented as a collar-gluing
    %
    \begin{equation}
        S^1 \cong \mathbb{R} \coprod\limits_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod\limits_{\bar{\mathbb{R}}\sqcup \mathbb{R}} \mathbb{R},
    \end{equation}
    %
    where $\bar{\mathbb{R}}$ denotes $\mathbb{R}$ with the opposite orientation to the standard one. Factorization homology then gives
    %
    \begin{equation}
        \int_{S^1} A \simeq \int_{\mathbb{R}} A \bigotimes\limits_{\int_{\mathbb{R}} A \otimes \int_{\bar{\mathbb{R}}} A} \int_{\mathbb{R}} A \simeq A \bigotimes\limits_{A \otimes A^{\mathsf{op}}} A,
    \end{equation}
    %
    where the result is known in the literature as the Hochschild homology (or more properly chains) of the associative algebra $A$.
\end{example}

@@

All of the above statements about factorization homology and disk algebras did not rely heavily on the stratified structure which we introduced them with. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_sructure}.

>>>>

    In more details, following \cite[ex.2.5]{aft_fhstrat}, objects of $\disk(\bstr)_{/M}$ are finite sets of open embeddings of disks $(U \xhookrightarrow{} M)$. A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$. A morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
\end{remark}

\begin{remark}
    The constructions of the slice category also holds, word for word, in the case of $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. The fact that they are $\infty$-operads is also true. The key difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e. finite sets of open embeddings into $M$. However, the morphisms now contain less information. A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. This also holds for higher arity morphisms too.

    That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both $\infty$-operads $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

@@

We now focus on describing disk algebras over oriented intervals (or equivalently, framed intervals) with and without boundary. Not only is this an important example for what disk algebras look like, but it's also important in defining what it means to say that factorization homology is excisive. The following constructions can be found in the originals \cite{af_fhtop,aft_fhstrat}.

We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically. For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.

@@

\begin{proposition}\label{prop:disk1bor=assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories between $\mathsf{D}_1^{\partial, *}$-structured disks and the symmetric monoidal envelope of $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, *}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow[\simeq]{\ \ [-] \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}}).
    \end{equation}
    %
    The functor $[-]$ assigns $[\hoint] = R$, $[\mathbb{R}] = A$ and $[\mathbb{R}_{\leq 0}] = L$.
\end{proposition}

@@

\begin{proposition}\label{prop:disk1bor_over_int=ORL}
    There are equivalences of $\infty$-operads
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
    \end{equation}
    %
    that descend to the equivalences of \cref{prop:disk1bor=assocRL}.
\end{proposition}

\begin{proof}
    As in the proof of \cref{prop:disk1bor=assocRL} the first equivalence is clear. The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$. These are then clearly the objects that map to the respective distinguished subsets. Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijection on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented. It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:env_ORL=env_assocRL}
    There are equivalences of symmetric monoidal $\infty$-categories
    %
    \begin{equation}
        \mathsf{Env}(\mathsf{O^{RL}}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env}(\disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]}) \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{\ \ \simeq \ \ } \mathsf{Env} (\mathsf{Assoc^{RL}})
    \end{equation}
\end{proposition}

@@

    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, *})$. There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty. This functor is final\footnote{A functor $F: \catC \xrightarrow{} \mathscr{D}$ between $\infty$-categories is final if precomposition with it preserves colimits \[ \mathsf{colim}(G \circ F) \simeq \mathsf{colim}(G).\]} because adjoining a minimum and maximum gives a left adjoint to it. We recognize the simplicial object
    %
    \begin{equation}
        \mathsf{B}_{\bullet}(R, A, L): \Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}} \simeq \mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC
    \end{equation}
    %
    as the two-sided bar construction. Since $\catC$ has colimits and $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ is final, the geometric realization of the above is
    %
    \begin{equation}
        \mathsf{B} (R, A, L) \equiv R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
    \end{equation}
    %
    To show the naturality of these equivalences, in the algebra variable, consider the algebra map $(F \xrightarrow{f} G) \in \mathsf{Fun}(\disk_{/[-1,1]}, \catC)$. We can consider the colimit as a functor
    %
    \begin{equation}
        \mathsf{colim}: \mathscr{C} \mathsf{at}_{\infty / \catC} \xrightarrow{} \catC,
    \end{equation}
    %
    such that the equivalences arise from composing with the adjoints $\Delta^{\mathsf{op}} \mathrel{\substack{\textstyle\leftarrow\\[-0.1ex]\textstyle\hookrightarrow}} \disk_{/[-1,1]}$. The naturality condition is then arranged by the functoriality of $\mathsf{colim}$, namely, by the images of the squares
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small]
            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] \arrow[dd, equal] & \disk_{/[-1,1]} \arrow[rd, "F"] \arrow[l, shift right] \arrow[dd, phantom, bend left = 60, "f"] \arrow[dd, equal] & \\
            & & \catC \\
            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] & \disk_{/[-1,1]} \arrow[ru, "G"'] \arrow[l, shift right] &  
        \end{tikzcd}
    \end{equation}
    %
    over $\catC$.
\end{proof}

%\begin{proposition}[{\cite[prop.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
%    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$. Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{} \catC$. Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
%    %
%    \begin{equation}
%        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
%    \end{equation}
%\end{proposition}

@@

\begin{proof}
    The definition comes with a claim that the canonical morphism in $\catC$ exists. This we need to show. The data of a collar-gluing $f: M \xrightarrow{} [-1,1]$ allows us to pushforward $F$ to
    %
    \begin{equation}
        f_*F: \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
    \end{equation}
    %
    By \cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$. Further using \cref{prop:barconst=intinterval} we have
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{f(M_0 \times \mathbb{R})}  F(M_+)\simeq \int_{[-1,1]} f_* F \xrightarrow{\quad} F (f^{-1}[-1,1]) = F(M),
    \end{equation}
    %
    where the morphism is given by the fact that factorization homology is a colimit.
\end{proof}

@@

    The first nontrivial example is then the oriented circle. We know that the algebras that we will be evaluating with are $\disk (\mathsf{D}_1^{\partial, *})$-algebras (or even simpler the restriction to $\disk (\mathsf{D}_1^{*})$ the ones without boundary). The oriented circle can be presented as a collar-gluing
    %
    \begin{equation}
        S^1 \cong \mathbb{R} \coprod\limits_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod\limits_{\bar{\mathbb{R}}\sqcup \mathbb{R}} \mathbb{R},
    \end{equation}
    %
    where $\bar{\mathbb{R}}$ denotes $\mathbb{R}$ with the opposite orientation to the standard one. Factorization homology then gives
    %
    \begin{equation}
        \int_{S^1} A \simeq \int_{\mathbb{R}} A \bigotimes\limits_{\int_{\mathbb{R}} A \otimes \int_{\bar{\mathbb{R}}} A} \int_{\mathbb{R}} A \simeq A \bigotimes\limits_{A \otimes A^{\mathsf{op}}} A,
    \end{equation}
    %
    where the result is known in the literature as the Hochschild homology (or more properly chains) of the associative algebra $A$.
\end{example}

@@

All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}. We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.

### 2023-12-19 sections/3algebras.tex
Add files via upload

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies the following condition:
    %
    \begin{enumerate}
        \item Denote by $f: \bsc_{/M} \xrightarrow{} \bsc$ the forgetful functor. For all $U, V \in \bsc_{/M}$
        %
        \begin{equation}
            f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V).
        \end{equation}
    \end{enumerate} 
\end{definition}

@@

\subsection{Factorization Algebras on Euclidean spaces}\label{ssec:lcfa_on_Rn}

@@

\begin{proposition}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
    \end{equation}
\end{proposition}

>>>>

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
    %
    \begin{equation}
        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
    \end{equation}
    %
    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
\end{definition}

@@

\subsection{Factorization Algebras on Euclidean Spaces}\label{ssec:lcfa_on_Rn}

@@

\begin{proposition}\label{prop:dunn_additivity}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
    \end{equation}
\end{proposition}

### 2023-12-19 sections/4gluing.tex
Add files via upload

\begin{example}{\color{red} GO TO LATER CHAPTER}
    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing. Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$. The result then simplifies to
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
    \end{equation}
    %
    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
\end{example}

>>>>

\begin{example}
    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$. The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist. Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1^{\mathsf{op_f}} \arrow[r, phantom, "\simeq", description] & B^{\mathsf{op_f}} \\
            A \arrow[ru, phantom, "\simeq", sloped, description] \arrow[rd, phantom, "\simeq", sloped, description] & & & \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 \arrow[r, phantom, "\simeq", description] & B,
        \end{tikzcd}
    \end{equation}
    %
    where $^{\mathsf{op_f}}$ is the opposite functor in the fiber direction. Thus, instead of an $\mathbb{E}_1$-\emph{self}-equivalence we have an equivalence with the opposite algebra.

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of Dunn additivity \cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}

%\begin{example}{\color{red} GO TO LATER CHAPTER}
%    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing. Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$. The result then simplifies to
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
%    \end{equation}
%    %
%    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
%\end{example}

### 2023-12-19 sections/5classification.tex
Add files via upload

We will see that the case of $d=0$ is of particular importance. This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. To get a better grasp on this case we examine the $\infty$-operad.

@@

@@

>>>>

In fact, technically, the only case we need to consider is when $d=0$. This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
%
\begin{equation}
    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
\end{equation}
%
together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. To get a better grasp on $\mathbb{R}^n_*$ case we examine the $\infty$-operad.

@@

.....

@@

By .... $\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics. In the special case that $\Sigma$ is a stratum, $\mathsf{C}(\pi)$ is even a fiber bundle with fiber $\mathbb{R}^{n-d}_*$. Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.

There is a special case that we can already tackle, which is the case of framed manifolds. This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$. This, in turn implies a trivialization for $\mathsf{C}(\pi)$ as a bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$, i.e. there is an isomorphism
%
\begin{equation}
    \mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*.
\end{equation}

However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components. Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:ginot_classif_Rn*}, we already have the result that
%
\begin{equation}
    \lcfa_{\mathsf{C}(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}

Going from $\mathsf{C}(\pi)$ to $M_{\Sigma}$ we use the fact that the link is also trivialized, as already mentioned above, which tells us that
%
\begin{equation}
    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\Sigma \times (\mathbb{R} \setminus \{0\})} (\catC),
\end{equation}
%
and finally, that
% 
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}

Apart from confirming our previous observations that what is encoded is an algebra away from the defect, and algebra on the defect and a module structure relating them, this now exactly specifies what that module structure should be given by.
